Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-05-17 paper.tex
more responses to comments

We develop a hybrid architecture for inferring graphics programs.  Our
approach uses a deep neural network infer an execution trace from an
image; this network recovers primitive drawing operations such as
lines, circles, or arrows, along with their parameters. For added
robustness, we use the deep network as a proposal distribution for a
stochastic search over execution traces.  Finally, we use program synthesis to recover the program from its
trace.  The program synthesizer discovers constructs such as loops and
geometric operations such as reflections and affine transformations.
% \remark{This paragraph is all about making things a bit more specific,
%   so you really need more specifics about program synth here.}

Each of these three components -- the deep network, the stochastic
search, the program synthesizer -- confers its own advantages. From
the deep network, we get a fast system that can recover plausible
execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference...}. From the stochastic search, we get
added robustness: essentially, the stochastic search can correct
mistakes made by the deep network's proposals.  From the program
synthesizer, we get abstraction: our system recovers coordinate
transformations, for loops, and subroutines, which are useful for
downstream tasks and can help correct some mistakes of the earlier stages.
% \remark{I wonder if this would work even better as a bulleted list...}
\remark{Tie these claims into the paper results: state what the `downstream' tasks are that you actually do, and refer to the sections where they occur}

@@

%% When we
%% have the generative model (the rendering function) and treat the trace
%% as fully observed, we need not solve an unsupervised or reinforcement
%% learning problem.
\tikzset{>=latex}
\begin{figure}
  \begin{tikzpicture}
  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(T)$] (canvas) at (0,-4) {};
  \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
  % draw partial image on canvas
  \draw (0.5cm,-4cm) circle (0.1875cm);
  \draw (1.2cm,-4.3) circle (0.1875cm);
  \draw (0.85cm,-4.6) circle (0.1875cm);

@@

\section{Synthesizing graphics programs from execution traces}
Although the execution trace of a graphics program describes the parts
of a scene, it fails to encode higher-level features of the image,
such as repeated motifs or symmetries.  A \emph{graphics
  program} better describe structures like these,
and we now take as our goal to synthesize simple graphics programs from
their execution traces.

>>>>

We develop a hybrid architecture for inferring graphics programs.  Our
approach uses a deep neural network infer an execution trace from an
image; this network recovers primitive drawing operations such as
lines, circles, or arrows, along with their parameters. For added
robustness, we use the deep network as a proposal distribution for a
stochastic search over execution traces.  Section~\ref{neuralNetworkSection} describes this first stage of the architecture where we infer drawing commands from images, and explains how we handle noisy hand drawings.
Finally, we use program synthesis techniques to recover the program from its
trace.  The program synthesizer discovers constructs such as loops and
geometric operations such as reflections and affine transformations.
% \remark{This paragraph is all about making things a bit more
Section~\ref{programSynthesisSection} describes how the architecture
synthesizes programs from execution traces,
and how those programs are used for measuring similarity between hand drawings,
extrapolating figures, and correcting errors made by the deep network.

%   so you really need more specifics about program synth here.}

%% Each of these three components -- the deep network, the stochastic
%% search, the program synthesizer -- confers its own advantages. From
%% the deep network, we get a fast system that can recover plausible
%% execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference...}. From the stochastic search, we get
%% added robustness: essentially, the stochastic search can correct
%% mistakes made by the deep network's proposals.  From the program
%% synthesizer, we get abstraction: our system recovers coordinate
%% transformations, for loops, and subroutines, which are useful for
%% downstream tasks and can help correct some mistakes of the earlier stages.
%% % \remark{I wonder if this would work even better as a bulleted list...}
%% \remark{Tie these claims into the paper results: state what the `downstream' tasks are that you actually do, and refer to the sections where they occur}

@@

%% When we
%% have the generative model (the rendering function) and treat the trace
%% as fully observed, we need not solve an unsupervised or reinforcement
%% learning problem.
\tikzset{>=latex}
\begin{figure}
  \begin{tikzpicture}
  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(T)$] (canvas) at (0,-4) {};
  \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
  % draw partial image on canvas
  \draw (0.375cm,-3.25cm) circle (0.125cm);
  \draw (0.625cm,-3.625) circle (0.125cm);
  \draw (0.75cm,-3.375) circle (0.125cm);

@@

\section{Synthesizing graphics programs from execution traces}\label{programSynthesisSection}
Although the execution trace of a graphics program describes the parts
of a scene, it fails to encode higher-level features of the image,
such as repeated motifs or symmetries.  A \emph{graphics
  program} better describe structures like these,
and we now take as our goal to synthesize simple graphics programs from
their execution traces.
